A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-22 response.tex

\vspace*{1em} \noindent \textit{\textbf{R2:} 2. Line 15 on page 7: "We found it crucial to record" $\rightarrow$ it is crucial.}

\vspace*{1em} \noindent \textbf{Response:} fixed \\ \\

\vspace*{1em} \noindent \textit{\textbf{R2:} 3. The authors picked 50 datapoints for each cluster. Are there any particular reasons for choosing 50? There are very few clusters with more than 50 datapoints. A more reasonable method is to inspect all datapoints.}

\vspace*{1em} \noindent \textbf{Response:} Our analysis revealed many clusters (39 in total) with more than 50 datapoints. More specifically, one cluster has 618 datapoints, four clusters more than 300 datapoints, and 15 clusters more than 100 datapoints. With our number of datapoints, manual inspection would be overwhelmingly time-consuming.

@@

We believe that the choice of 50 datapoints per cluster successfully balances ensuring that the selected datapoints truly represent the same change and making manual inspection feasible. Our sample size allows us to get meaningful insights into the characteristics of each cluster. \\ \\

\vspace*{1em} \noindent \textit{\textbf{R2:} 4. Line 6 on page 14: "A human analyzer (paper author) compares the actual change in the code and compares it to the visual representation of the respective data point." $\rightarrow$ A human analyzer (paper author) inspects the actual change … and compares it with the visual representation …}

\vspace*{1em} \noindent \textbf{Response:} fixed \\ \\

\vspace*{1em} \noindent \textit{\textbf{R2:} 5. What are the collected samples in the third paragraph of page 14 used for?}

\vspace*{1em} \noindent \textbf{Response:} We proposed a method to embed key AST information in a fixed-sized vector using a semi-automatically derived weighting scheme. RQ1 asks how successful we've been in terms of giving more values to the important elements in our ASTs. For instance, if in a code patch, the only change is adding \verb+.clone()+, then we should expect the element \verb+clone+ to have the highest value. In RQ1, we sample 25 datapoints from General datapoints and 25 datapoints from BC-related datapoints (50 in total) to manually analyze whether the values in their code vector actually respect the important elements in the AST. Note that we selected 50 datapoints that minimize the sampling error, i.e. it is a low bias sampling. \\ \\

\vspace*{1em} \noindent \textit{\textbf{R2:} 6. I don't understand the sentence at line 25 of page 23. Particularly, what string formatting methods are gone through if using p instead of *p?}

\vspace*{1em} \noindent \textbf{Response:} fixed, added Clippy reference in the paper.

### 2023-06-22 response.tex

\subsection{Methodology \& Experiments}

In response to reviewer questions about methodology and experiments, we further explain our methodology and discuss why we made the choices we did. We summarize here, but invite the reviewers to read our full responses in Section~\ref{sec:detailed} of this response. We hope that the reviewers can better understand why we believe our choices to be appropriate. (Hyperlinked references in this document refer to parts of the response, while un-linked references are to the paper).\\

Reviewer 1:
\begin{itemize}
    \item Order information: our dataset is not large enough to incorporate it (\ref{rev:1:order}).
    \item Ignoring terminal tokens: including information about terminals would have led to dimensionality in the millions, which would be infeasible in terms of computational complexity (\ref{rev:1:terminal}). 
    \item RQ1: we have included qualitative comparisons of our approach with previous approaches and discussed how our approach is superior to those approaches. (\ref{rev:1:rq1}).
\end{itemize}

Reviewer 2:
\begin{itemize}
    \item Context: we believe our results show that context is not required to get meaningful results (\ref{rev:2:embedding}).
    \item Leaf nodes and penalizing large diffs: any clustering approach is going to have trouble clustering together large diffs, which have more ways to differ from each other than small diffs (\ref{rev:2:embedding}). 
    \item Picking 50 datapoints: manually evaluating large clusters is infeasible---e.g. we do not have the resources to evaluate clusters with order-of-618 datapoints manually (\ref{rev:2:minor}).
\end{itemize}

@@

In summary, we believe that we have made the best possible design decisions given limitations in datasets and resources available to us, and that our results are strong enough that they support our decisions.

\subsection{Discussion}

We wholeheartedly agree that it is important to show that the identified patterns are valuable. We have added an all-new Section 4.1, “Patterns Present and Missing” (specifically discussing the value of the top 10 patterns and summarizing our learnings) and mostly-new content in Section 4.2 “Usefulness of Rust Bug Patterns” (discussing the general usefulness of patterns), as well as paragraphs on actionability to 6 of the groups of patterns.

### 2023-10-31 response.tex

\usepackage{cite}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{todonotes}

\title{Response to Reviewer Comments}
\date{2023 November}
\author{Mohammad Robati Shirzad and Patrick Lam}
\begin{document}

\maketitle

Please find below our response to the reviews for our EMSE submission ``A Study of Common Bug Fix Patterns in Rust''.

\section{Reviewer 1}

\textit{I appreciate the authors' efforts in improving the paper, and most of my concerns have been addressed.}

\subsection{Reorganizing related work}

\textit{\textbf{R1:} I have observed that the related work now includes several subsections focusing on APR and patch correctness prediction. It would be beneficial to reorganize and consolidate these subsections into a single coherent section. Furthermore, the section on related work should encompass studies related to bug classification in programming languages with a longer history.}

\vspace*{1em} \noindent \textbf{Response:} \todo{Probably no need for argument, let's just do what he asks.}

\subsection{More discussion on the impact of the evolving Rust specification}

\textit{\textbf{R1:} Additionally, I would appreciate it if the authors could discuss the potential impact of the evolving Rust specification. Given that Rust is a novel programming language, it is subject to rapid grammatical changes, which in turn could influence bug characteristics and symptoms.}

\vspace*{1em} \noindent \textbf{Response:} \todo{Probably no need for argument, let's just do what he asks.}

\section{Reviewer 2}

\textit{Thanks a lot for the information and clarification in the rebuttal and the new paper version. I would suggest the authors make the following changes in the next paper version.}

\subsection{More discussion on the size and type of the patches}

\textit{\textbf{R2:} Inspired by the last paragraph of Section 4.1, can authors discuss which of the following is more important for Rust in the next paper version: fixing bugs and fixing compilation errors?}

\vspace*{1em} \noindent \textbf{Response:} \todo{Need some argument here and some changes in the text.}

\vspace*{1em} \noindent \textit{\textbf{R2:} Please discuss why identified patches are all small in the next paper version. Basically, please add the last paragraph of Section 2.2.4 of the rebuttal to the next paper version.}

\vspace*{1em} \noindent \textbf{Response:} \todo{Probably just do what he asks.}

\subsection{Paraphrasing and providing clearer explanation}

\textit{\textbf{R2:} In Section 2.3.2, the authors use sentences from an existing paper directly (although quotes are added). I don't think this is a good way to write an academic paper. Please paraphrase these sentences.}

\vspace*{1em} \noindent \textbf{Response:} \todo{No argument, just paraphrase.}

\vspace*{1em} \noindent \textit{\textbf{R2: } I still do not understand Figure 1. I suggest the authors label ASTDiff nodes with code to ease the explanation.}

\vspace*{1em} \noindent \textbf{Response:} \todo{First, we need some changes in paper text to make it clearer. Then, need some explanation here how we've changed it.}

\subsection{Minor issues}

\textit{\textbf{R2:} Line 21 on page 8: work around -> workaround}

\vspace*{1em} \noindent \textbf{Response:} Fixed.

\vspace*{1em} \noindent \textit{\textbf{R2:} Line 49 on page 8: which path is colored in purple in figure 1?}

\vspace*{1em} \noindent \textbf{Response:} It is the rightmost path. We changed the color to blue so it is clearer.
